Structures Report

### 2017-04-02 mu/structures-report/structures-report.tex
Making chi layer by layer
mag inc alg color zones completed for all structures.
aa and ab atomic structures completed

\section{Up (graphone)} % (fold)
\label{sec:up}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{$\mathcal{V}^{\mathrm{xb}}$ energy range 0.0--0.2 eV }
\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-magvxb-incang-1-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
    40$^{\circ}$.}
    \label{fig:up-magvxbincang1}
\end{figure}
\begin{figure}[h]
    \centering
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-xx-angcomp.pdf}
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-xy-angcomp.pdf}\\
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-xz-angcomp.pdf}
    \caption{Cheking angle of incidence for $xb$ components for up structure.}
    \label{fig:up-xbangcomp}
\end{figure}
\begin{figure}[tb]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vab-xb-1.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 40$^{\circ}$.}
    \label{fig:up-vxb1}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-absvab-1.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
    \label{fig:up-xbybcomp-1}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-absvab-2.pdf}
    % \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
    \label{fig:up-xbybcomp-2}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$\mathcal{V}^{\mathrm{xb}}$}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-magvxb-incang-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
    145$^{\circ}$.}
    \label{fig:alt-magvxbincang}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxx.pdf}
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxy.pdf}\\
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxz.pdf}
    \caption{Cheking angle of incidence for $xb$ components.}
    \label{fig:alt-xbangcomp}
\end{figure}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-vab-xb.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 145$^{\circ}$.}
    \label{fig:alt-vxb1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$\mathcal{V}^{\mathrm{yb}}$}
\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-magvyb-incang-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
    145$^{\circ}$.}
    \label{fig:alt-magvybincang1}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxx.pdf}
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxy.pdf}\\
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxz.pdf}
    \caption{Cheking angle of incidence for $yb$ components.}
    \label{fig:alt-ybangcomp}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-vab-yb.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 145$^{\circ}$.}
    \label{fig:alt-vyb1}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-absvab.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
    \label{fig:alt-xbybcomp}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.3\textwidth]{../hnbGh-aa/hnbGh-aa-figures/hnbGh-aa-2}
    \caption{HNBC$_{2}$H-aa structure}
    \label{fig:aastruc}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$\mathcal{V}^{\mathrm{xb}} $}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-magvxb-incang-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
    155$^{\circ}$.}
    \label{fig:aa-magvxbincang}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vxx.pdf}
    \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vxy.pdf}\\
    \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vxz.pdf}
    \caption{Cheking angle of incidence for $xb$ components. There is a
    different angle for each component to have the most intense response.}
    \label{fig:aa-xbangcomp}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-magvxb.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ for different
    polarization angles.}
    \label{fig:aa-magvxb}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vxb-1.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 155$^{\circ}$.}
    \label{fig:aa-vxb1}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-absvab.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$.}    
    \label{fig:aa-xbybcomp}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.3\textwidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-2}
    \caption{HNBC$_{2}$H-ab structure}
    \label{fig:abstruc}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$\mathcal{V}^{\mathrm{xb}} $}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-magvxb-incang-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
    155$^{\circ}$.}
    \label{fig:ab-magvxbincang}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vxx.pdf}
    \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vxy.pdf}\\
    \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vxz.pdf}
    \caption{Cheking angle of incidence for $xb$ components. There is a
    different angle for each component to have the most intense response.}
    \label{fig:ab-xbangcomp}
\end{figure}

@@

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-absvab.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$.}    
    \label{fig:ab-xbybcomp}
\end{figure}

>>>>

\section{Up (graphone)} % (fold)
\label{sec:up}
figure
%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{$\mathcal{V}^{\mathrm{xb}}$ energy range 0.0--0.2 eV }
\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-magvxb-incang-1-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
    40$^{\circ}$.}
    \label{fig:up-magvxbincang1}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-xx-angcomp.pdf}
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-xy-angcomp.pdf}\\
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-xz-angcomp.pdf}
    \caption{Cheking angle of incidence for $xb$ components for up structure.}
    \label{fig:up-xbangcomp}
\end{figure}
\begin{figure}[tb]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vab-xb-1.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 40$^{\circ}$.}
    \label{fig:up-vxb1}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-absvab-1.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
    \label{fig:up-xbybcomp-1}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-absvab-2.pdf}
    % \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
    \label{fig:up-xbybcomp-2}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$\mathcal{V}^{\mathrm{xb}}$}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-magvxb-incang-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
    145$^{\circ}$.}
    \label{fig:alt-magvxbincang}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxx.pdf}
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxy.pdf}\\
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxz.pdf}
    \caption{Cheking angle of incidence for $xb$ components.}
    \label{fig:alt-xbangcomp}
\end{figure}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-vab-xb.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 145$^{\circ}$.}
    \label{fig:alt-vxb1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$\mathcal{V}^{\mathrm{yb}}$}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-magvyb-incang-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
    145$^{\circ}$.}
    \label{fig:alt-magvybincang1}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxx.pdf}
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxy.pdf}\\
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxz.pdf}
    \caption{Cheking angle of incidence for $yb$ components.}
    \label{fig:alt-ybangcomp}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-vab-yb.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 145$^{\circ}$.}
    \label{fig:alt-vyb1}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-absvab.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
    \label{fig:alt-xbybcomp}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.45\textwidth]{../hnbGh-aa/hnbGh-aa-figures/hnbGh-aa-1}
    \includegraphics[width=0.45\textwidth]{../hnbGh-aa/hnbGh-aa-figures/hnbGh-aa-2}
    \caption{HNBC$_{2}$H-aa structure}
    \label{fig:aastruc}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$\mathcal{V}^{\mathrm{xb}} $}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-magvxb-incang-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
    155$^{\circ}$.}
    \label{fig:aa-magvxbincang}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vxx.pdf}
    \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vxy.pdf}\\
    \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vxz.pdf}
    \caption{Cheking angle of incidence for $xb$ components. There is a
    different angle for each component to have the most intense response.}
    \label{fig:aa-xbangcomp}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-magvxb.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ for different
    polarization angles.}
    \label{fig:aa-magvxb}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vxb-1.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 155$^{\circ}$.}
    \label{fig:aa-vxb1}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-absvab.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$.}    
    \label{fig:aa-xbybcomp}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.45\textwidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-1}
    \includegraphics[width=0.45\textwidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-2}
    \caption{HNBC$_{2}$H-ab structure}
    \label{fig:abstruc}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$\mathcal{V}^{\mathrm{xb}} $}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-magvxb-incang-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
    155$^{\circ}$.}
    \label{fig:ab-magvxbincang}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vxx.pdf}
    \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vxy.pdf}\\
    \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vxz.pdf}
    \caption{Cheking angle of incidence for $xb$ components. There is a
    different angle for each component to have the most intense response.}
    \label{fig:ab-xbangcomp}
\end{figure}

@@

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=0.7\textwidth]{}
%     \caption{Layer decomposition for the most intense response:
%     $\mathcal{V}^{\mathrm{yz}}$.}
%     \label{fig:ab-lay}
% \end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-absvab.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$.}    
    \label{fig:ab-xbybcomp}
\end{figure}
